What Does Reproducible Research Mean for Plant Pathology?

### 2016-09-05 README.rmd
Restructure file names, add new references and materials, update style reference
Added several new references to the bibliography

Added new material to manuscript outline to start fleshing out the
materials

Moved the document from README.Rmd to What Does Reproducible Research
Mean for Plant Pathology.Rmd

README.Rmd produces a GitHub Markdown document and will contain the
abstract and links to the MS Word document and Rmd file used to
generate it

## WHAT IS REPRODUCICBLE RESEARCH?

**Definitions.** Reproducible research
Replicable research

## WHY REPRODUCIBLE RESEARCH?

## HOW TO MAKE REPRODUCIBLE RESEARCH
Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.

@@

>>>>

# MAIN TEXT
Reproductibility and replicability in scientific research have once again been
highlighted recently [@Nature_Editorial_2016; @Baker2016a] as an issue.

Patil et al. [-@Patil066803] have provided several definitions to clarify the
concepts surrounding reproducibility and replicability. For the purposes of this
paper we follow the definitions as given by Patil et al. [-@Patil066803].

* Why reproducible research

## BEST METHODS FOR REPRODUCIBLE RESEARCH
* Provide definitions (provide defintions for terms used so it's clear)
* Data
  * Data formatting (flat files; use Comma Chameleon, Table Tool, others?)
  * Data storage (don't edit raw data files; use file permissions to prevent changes to raw data files, use data bases where possible and appropriate; etc.)
* When publishing
  * Provide data
  * Provide code
* Using GitHub for code (and small data?)
* Using Figshare or Zenodo vs a lab website (DOIs, other reasons)

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide 
[http://adamhsparks.github.io/MICCORDEA/](models, data and code) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide 
[http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/](models, data and code)
necessary to replicate model development and the subsequent the study on the effects
of climate change on potato late blight.
* Other examples from plant pathology providing e-Xtras or supplemental material

@@

### Notes
https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/

### 2016-09-05 What Does Reproducible Research Mean for Plant Pathology.Rmd
Restructure file names, add new references and materials, update style reference
Added several new references to the bibliography

Added new material to manuscript outline to start fleshing out the
materials

Moved the document from README.Rmd to What Does Reproducible Research
Mean for Plant Pathology.Rmd

README.Rmd produces a GitHub Markdown document and will contain the
abstract and links to the MS Word document and Rmd file used to
generate it

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "5 July 2016"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
    keep_md: TRUE
bibliography: bibliography.bib
csl: phytopathology.csl
---

>>>>

---
title: "What Does Reproducible Research Mean for Plant Pathology?"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
bibliography: bibliography.bib
csl: phytopathology.csl
---
